\LARGE Untangling the link between traits, size and growth rate in plants

### 2015-04-29 fig2.tex
panels for conceptual figure #37

\defineRow{0}{thisrow}
\rowtitle{Biomass production}
\firstcol{1}{$\frac{\textrm{d}P}{\textrm{d}t}$}{figures/empty_box}{}
\othercol{2}{$Y$}{figures/empty_box}{$\times$}
\othercol{3}{$\Bigg(A$}{figures/empty_box}{-}
\othercol{4}{\ $R$}{figures/empty_box}{$\Bigg)$}
\othercol{5}{$-T$}{figures/empty_box}{}
\rowlabel{(1)}

\defineRow{1}{thisrow}
\rowtitle{Construction costs}
\firstcol{1}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}m_{\textrm{t}}}$}{figures/empty_box}{$\Bigg($}
\othercol{2}{$\frac{\textrm{d}m_{\textrm{l}}}{\textrm{d}a_{\textrm{l}}}$}{figures/empty_box}{+}
\othercol{3}{$\frac{\textrm{d}m_{\textrm{ss}}}{\textrm{d}a_{\textrm{l}}}$}{figures/empty_box}{+}
\othercol{4}{$\frac{\textrm{d}m_{\textrm{sb}}}{\textrm{d}a_{\textrm{l}}}$}{figures/empty_box}{+}
\othercol{5}{$\frac{\textrm{d}m_{\textrm{r}}}{\textrm{d}a_{\textrm{l}}}$}{figures/empty_box}{$\Bigg)^{-1}$}
 \rowlabel{(2)}

\defineRow{2}{thisrow}
\rowtitle{Leaf-area growth}
\firstcol{1}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}t}$}{figures/empty_box}{}
\othercol{2}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}m_{\textrm{t}}}$}{figures/empty_box}{$\times$}
\othercol{3}{$\frac{\textrm{d}m_{\textrm{t}}}{\textrm{d}P}$}{figures/empty_box}{$\times$}
\othercol{4}{$\frac{\textrm{d}P}{\textrm{d}t}$}{figures/empty_box}{}
\rowlabel{(3)}

\defineRow{3}{thisrow}
\rowtitle{Height growth}
\firstcol{1}{$\frac{\textrm{d}h}{\textrm{d}t}$}{figures/empty_box}{}
\othercol{2}{$\frac{\textrm{d}h}{\textrm{d}a_{\textrm{l}}}$}{figures/empty_box}{$\times$}
\othercol{3}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}t}$}{figures/empty_box}{}
\rowlabel{(4)}

\defineRow{4}{thisrow}
\rowtitle{Basal-area growth}
\firstcol{1}{$\frac{\textrm{d}a_{\textrm{st}}}{\textrm{d}t}$}{figures/empty_box}{}
\othercol{2}{$\frac{\textrm{d}a_{\textrm{ss}}}{\textrm{d}a_{\textrm{l}}}$}{figures/empty_box}{$\times$}
\othercol{3}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}t}$}{figures/empty_box}{+}
\othercol{4}{$\frac{\textrm{d}a_{\textrm{sh}}}{\textrm{d}t}$}{figures/empty_box}{}
\rowlabel{(5)}

\defineRow{5}{thisrow}
\rowtitle{Diameter growth}
\firstcol{1}{$\frac{\textrm{d}D}{\textrm{d}t}$}{figures/empty_box}{}
\othercol{2}{$\frac{\sqrt{\pi}}{\sqrt{a_{\textrm{st}}}}$}{figures/empty_box}{$\times$}
\othercol{3}{$\frac{\textrm{d}a_{\textrm{st}}}{\textrm{d}t}$}{figures/empty_box}{}
\rowlabel{(6)}

>>>>

\defineRow{0}{thisrow}
\rowtitle{Biomass production}
\firstcol{1}{$\frac{\textrm{d}P}{\textrm{d}t}$}{figures/F2_mass_production_net_production}{}
\othercol{2}{$Y$}{figures/empty_box}{$\times$}
\othercol{3}{$\Bigg(A$}{figures/F2_mass_production_assimilation}{-}
\othercol{4}{\ $R$}{figures/F2_mass_production_respiration}{$\Bigg)$}
\othercol{5}{$-T$}{figures/F2_mass_production_turnover}{}
\rowlabel{(1)}

\defineRow{1}{thisrow}
\rowtitle{Construction costs}
\firstcol{1}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}m_{\textrm{t}}}$}{figures/F2_leaf_area_growth_leaf_fraction}{$\Bigg($}
\othercol{2}{$\frac{\textrm{d}m_{\textrm{l}}}{\textrm{d}a_{\textrm{l}}}$}{figures/empty_box}{+}
\othercol{3}{$\frac{\textrm{d}m_{\textrm{ss}}}{\textrm{d}a_{\textrm{l}}}$}{figures/empty_box}{+}
\othercol{4}{$\frac{\textrm{d}m_{\textrm{sb}}}{\textrm{d}a_{\textrm{l}}}$}{figures/empty_box}{+}
\othercol{5}{$\frac{\textrm{d}m_{\textrm{r}}}{\textrm{d}a_{\textrm{l}}}$}{figures/empty_box}{$\Bigg)^{-1}$}
 \rowlabel{(2)}

\defineRow{2}{thisrow}
\rowtitle{Leaf-area growth}
\firstcol{1}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}t}$}{figures/F2_leaf_area_growth_dleaf_area_dt}{}
\othercol{2}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}m_{\textrm{t}}}$}{figures/F2_leaf_area_growth_leaf_fraction}{$\times$}
\othercol{3}{$\frac{\textrm{d}m_{\textrm{t}}}{\textrm{d}P}$}{figures/F2_leaf_area_growth_leaf_fraction}{$\times$}
\othercol{4}{$\frac{\textrm{d}P}{\textrm{d}t}$}{figures/F2_leaf_area_growth_net_production}{}
\rowlabel{(3)}

\defineRow{3}{thisrow}
\rowtitle{Height growth}
\firstcol{1}{$\frac{\textrm{d}h}{\textrm{d}t}$}{figures/F2_height_growth_height_growth_rate}{}
\othercol{2}{$\frac{\textrm{d}h}{\textrm{d}a_{\textrm{l}}}$}{figures/F2_height_growth_dheight_dleaf_area}{$\times$}
\othercol{3}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}t}$}{figures/F2_leaf_area_growth_dleaf_area_dt}{}
\rowlabel{(4)}

\defineRow{4}{thisrow}
\rowtitle{Basal-area growth}
\firstcol{1}{$\frac{\textrm{d}a_{\textrm{st}}}{\textrm{d}t}$}{figures/F2_basal_growth_dbasal_area_dt}{}
\othercol{2}{$\frac{\textrm{d}a_{\textrm{ss}}}{\textrm{d}a_{\textrm{l}}}$}{figures/empty_box}{$\times$}
\othercol{3}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}t}$}{figures/F2_leaf_area_growth_dleaf_area_dt}{+}
\othercol{4}{$\frac{\textrm{d}a_{\textrm{sh}}}{\textrm{d}t}$}{figures/empty_box}{}
\rowlabel{(5)}

\defineRow{5}{thisrow}
\rowtitle{Diameter growth}
\firstcol{1}{$\frac{\textrm{d}D}{\textrm{d}t}$}{figures/F2_diameter_growth_dbasal_diam_dt}{}
\othercol{2}{$\frac{\sqrt{\pi}}{\sqrt{a_{\textrm{st}}}}$}{figures/empty_box}{$\times$}
\othercol{3}{$\frac{\textrm{d}a_{\textrm{st}}}{\textrm{d}t}$}{figures/F2_basal_growth_dbasal_area_dt}{}
\rowlabel{(6)}
